---
title: "Acoustic analysis"
author: "Elan Portner"
date: "12/3/2017"
output: html_document
---


```{r get necessary packages, include = FALSE}
# 1) clear workspace
rm(list = ls(all = TRUE)); 

# 2) load packages: (fyi, you probably don't need all of these for this code, but good ones to have for spatial R stuff...)
## if you need to install any, uncomment and run (shown are some examples below)...

library(ncdf4); library(ncdf)
library(RNetCDF)
library(raster)
library(maps)
library(mapdata)
library(maptools)
library(rgdal)
library(move)
library(mapproj)
library(sp)
require(dismo)
library(ggplot2)
library(ggmap)
library(RColorBrewer)
library(reshape2)
library(mapplots)
library(rgeos)
library(polyclip)
library(spatstat)
library(tidyverse)
library(Rmisc)

```



```{r get_data, include = FALSE}
#read in data file - see "~/Assigning_regions_to_acoustics.R" for code to assign data to regions
acoustics = read.csv("~/Documents/R/Dosidicus/acoustics/acousticdata_uper200m_with_regions.csv") 
acousticdata = acoustics
### remove outliers for preliminary figure to improve visualization###
I = which(log(acousticdata$NASC)>12|log(acousticdata$NASC)<0)
acousticdata = acousticdata[-I,]
acousticdata$fill = 1
### 9 data points removed with above code ###
```


```{r plot_cruise_track,include = FALSE}

##### plot google map overlaid with cruise tracks ######

#need to convert longitude back to E/W for plotting map with google
acousticdata$Lon_M = acousticdata$Lon_M - 360

#set bounds of map using coordinates of our data
bc_bbox <- make_bbox(lat = Lat_M, lon = Lon_M, data = acousticdata)
bc_bbox
#>       left     bottom      right        top 
#> -133.63297   47.92497 -122.33652   55.80833

# grab the maps from google
bc_big <- get_map(location = c(left =-117.04904, bottom = 22.41260, right = -104.20950, top = 34.77702), source = "google", maptype = "satellite")
#> Warning: bounding box given to google - spatial extent only approximate.
#> converting bounding box to center/zoom specification. (experimental)
#> Map from URL : http://maps.googleapis.com/maps/api/staticmap?center=51.86665,-127.98475&zoom=6&size=640x640&scale=2&maptype=terrain&language=en-EN&sensor=false


```

### Map of cruise track
```{r, echo = FALSE, warning = FALSE}
# plot the points and color them by sector
p <- ggmap(bc_big) + 
  geom_point(data = acousticdata, mapping = aes(x = Lon_M, y = Lat_M, color = region), size = 0.3, stroke = 0, alpha = 0.9)+
  guides(colour = guide_legend(override.aes = list(size=2, stroke=1.5)))

p

```

##### Data was subsetted by time of day (nighttime = 7pm-6am)
##### Boxplot of logNASC by cruise*region for data extracted from upper water column (10-200m) in 1km chunks
```{r summary_boxplot, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9}
### create vector of simplified labels 
cruises = c("", "", "W.05", "","", "", "W.07", "","", "", "S.07", "",
            "", "", "W.10", "","", "", "W.11", "","", "", "S.12", "",
            "", "", "S.13", "","", "", "W.14", "","", "", "S.14", "",
            "", "", "S.16", "","", "", "S.17", "")
cruises2 = c("W.05", "W.07", "S.07", "W.10","W.11", "S.12","S.13", "W.14","S.14","S.16","S.17")
# Plot boxplots of scattering area within each polygon by cruise 
cruisePoly <- ggplot(acousticdata, aes(cpoly, log(NASC), fill = region)) + geom_boxplot() 
cruisePoly = cruisePoly +scale_x_discrete(labels = cruises)+theme(axis.text.x=element_text(hjust=1))
cruisePoly = cruisePoly + labs(x="Cruise (Season.Year, where W = winter and S = summer)")
cruisePoly
```


```{r anova, echo=FALSE, include = FALSE}
###### run ANOVA(s) to examine with explanatory variables significantly affect backscattering
acousticdata$season = as.factor(acousticdata$season)
acousticdata$region = as.factor(acousticdata$region)
acousticdata$year = as.factor(acousticdata$year)
```

##### ANOVA model: (NASC ~ season*region*year)
```{r}
aov.acoustics.nasc <- aov(NASC ~ season*region*year, data = acousticdata)
summary(aov.acoustics.nasc)
```


#### Plot mean Sv by cruise
```{r, echo = FALSE, warning = FALSE, message=FALSE, fig.width=9, fig.height=9}
cruise_plot <- function(cruse, seas, yr){ # cntry <- "Canada"
  
  #browser()
#   png <- paste0("cruise", cruse, ".png")
#   cat("cruise_plot(", cruse, ") -> ", png, "\n")
#   
  g <- acousticdata %>%
    filter(cruise == cruse) %>%
    ggplot(aes(x=Sv_mean, group = cruise, fill = region)) +
    geom_histogram(aes(y = ..count../sum(..count..)), binwidth = 5, 
                   position = "identity", alpha = 0.2, color = "black") +
    scale_x_continuous(limits = c(-90, -50))+
    scale_y_continuous(limits = c(0, 0.7))+
    xlab("Mean Sv") + 
    ylab("Proportion")+ 
    ggtitle(paste0("Cruise", " ", cruse, " ", "-", " ", seas, " ", yr))
  # print(g)
#   ggsave(png, g)
}

fig1 <- cruise_plot("1", "Winter", "2005")
fig2 <- cruise_plot("2", "Winter", "2007")
fig3 <- cruise_plot("3", "Summer", "2007")
fig4 <- cruise_plot("4", "Winter", "2010")
fig6 <- cruise_plot("6", "Winter", "2011")
fig7 <- cruise_plot("7", "Summer", "2012")
fig8 <- cruise_plot("8", "Summer", "2013")
fig9 <- cruise_plot("9", "Winter", "2014")
fig10 <- cruise_plot("10", "Summer", "2014")
fig11 <- cruise_plot("11", "Summer", "2016")
fig12 <- cruise_plot("12", "Summer", "2017")

multiplot(fig1, fig2, fig3, fig4, fig6, fig7, fig8, fig9, fig10, fig11, fig12, cols = 3)

```

##### ANOVA model: (Sv_mean ~ cruise*region)
```{r}
aov.acoustics.sv2 <- aov(Sv_mean ~ cruise*region, data = acousticdata)
summary(aov.acoustics.sv2)
```

##### ANOVA model: (Sv_mean ~ season*region*year)
```{r}
aov.acoustics.sv <- aov(Sv_mean ~ season*region*year, data = acousticdata)
summary(aov.acoustics.sv)
```

##### Mean Sv by region, by cruise : Baja

```{r by_region, echo = FALSE, warning = FALSE, message=FALSE, fig.width=9, fig.height=9}
cruise_plot <- function(cruse, reg, seas, yr){ # cntry <- "Canada"
  
  #browser()
#   png <- paste0("cruise", cruse, ".png")
#   cat("cruise_plot(", cruse, ") -> ", png, "\n")
#   
  g <- acousticdata %>%
    filter(cruise == cruse) %>%
    filter(region == reg) %>% 
    ggplot(aes(x=Sv_mean, group = cruise)) +
    geom_histogram(aes(y = ..count../sum(..count..)), binwidth = 3, 
                   position = "identity", alpha = 0.2, color = "black", fill = "red") +
    scale_x_continuous(limits = c(-90, -50))+
    scale_y_continuous(limits = c(0, 0.55))+
    xlab("Mean Sv") + 
    ylab("Proportion")+ 
    ggtitle(paste0("Cruise", " ", cruse, " ", "-", " ", seas, " ", yr))
  # print(g)
#   ggsave(png, g)
}

fig1 <- cruise_plot("1", "Baja", "Winter", "2005")
fig2 <- cruise_plot("2", "Baja","Winter", "2007")
fig3 <- cruise_plot("3", "Baja","Summer", "2007")
fig4 <- cruise_plot("4", "Baja","Winter", "2010")
fig6 <- cruise_plot("6", "Baja","Winter", "2011")
fig7 <- cruise_plot("7", "Baja","Summer", "2012")
fig8 <- cruise_plot("8", "Baja","Summer", "2013")
fig9 <- cruise_plot("9", "Baja","Winter", "2014")
fig10 <- cruise_plot("10", "Baja","Summer", "2014")
fig11 <- cruise_plot("11", "Baja","Summer", "2016")
fig12 <- cruise_plot("12", "Baja","Summer", "2017")

multiplot(fig1, fig2, fig3, fig4, fig6, fig7, fig8, fig9, fig10, fig11, fig12, cols = 3)

```

##### ANOVA model subsetted by region:Baja (Sv_mean ~ cruise)
```{r anova_baja}
acousticdata_Baja = subset(acousticdata, region == "Baja")
acousticdata_Baja$cruise = as.factor(acousticdata_Baja$cruise)

aov.acoustics.sv2 <- aov(Sv_mean ~ cruise, data = acousticdata_Baja)
summary(aov.acoustics.sv2)

TukeyHSD(aov.acoustics.sv2)
```

##### Mean Sv by region, by cruise : Sonora

```{r by_region_sonora, echo = FALSE, warning = FALSE, message=FALSE, fig.width=9, fig.height=9}
cruise_plot <- function(cruse, reg, seas, yr){ # cntry <- "Canada"
  
  #browser()
#   png <- paste0("cruise", cruse, ".png")
#   cat("cruise_plot(", cruse, ") -> ", png, "\n")
#   
  g <- acousticdata %>%
    filter(cruise == cruse) %>%
    filter(region == reg) %>% 
    ggplot(aes(x=Sv_mean, group = cruise)) +
    geom_histogram(aes(y = ..count../sum(..count..)), binwidth = 3, 
                   position = "identity", alpha = 0.2, color = "black", fill = "blue") +
    scale_x_continuous(limits = c(-90, -50))+
    scale_y_continuous(limits = c(0, 0.55))+
    xlab("Mean Sv") + 
    ylab("Proportion")+ 
    ggtitle(paste0("Cruise", " ", cruse, " ", "-", " ", seas, " ", yr))
  # print(g)
#   ggsave(png, g)
}

fig1 <- cruise_plot("1", "Sonora", "Winter", "2005")
fig2 <- cruise_plot("2", "Sonora","Winter", "2007")
fig3 <- cruise_plot("3", "Sonora","Summer", "2007")
fig4 <- cruise_plot("4", "Sonora","Winter", "2010")
fig6 <- cruise_plot("6", "Sonora","Winter", "2011")
fig7 <- cruise_plot("7", "Sonora","Summer", "2012")
fig8 <- cruise_plot("8", "Sonora","Summer", "2013")
fig9 <- cruise_plot("9", "Sonora","Winter", "2014")
fig10 <- cruise_plot("10", "Sonora","Summer", "2014")
fig11 <- cruise_plot("11", "Sonora","Summer", "2016")
fig12 <- cruise_plot("12", "Sonora","Summer", "2017")

multiplot(fig1, fig2, fig3, fig4, fig6, fig7, fig8, fig9, fig10, fig11, fig12, cols = 3)

```

##### ANOVA model subsetted by region:Sonora (Sv_mean ~ cruise)
```{r anova_sonora}
acousticdata_Sonora = subset(acousticdata, region == "Sonora")
acousticdata_Sonora$cruise = as.factor(acousticdata_Sonora$cruise)

aov.acoustics.sv2 <- aov(Sv_mean ~ cruise, data = acousticdata_Sonora)
summary(aov.acoustics.sv2)

TukeyHSD(aov.acoustics.sv2)
```

##### Mean Sv by region, by cruise : Central

```{r by_region_central, echo = FALSE, warning = FALSE, message=FALSE, fig.width=9, fig.height=9}
cruise_plot <- function(cruse, reg, seas, yr){ # cntry <- "Canada"
  
  #browser()
#   png <- paste0("cruise", cruse, ".png")
#   cat("cruise_plot(", cruse, ") -> ", png, "\n")
#   
  g <- acousticdata %>%
    filter(cruise == cruse) %>%
    filter(region == reg) %>% 
    ggplot(aes(x=Sv_mean, group = cruise)) +
    geom_histogram(aes(y = ..count../sum(..count..)), binwidth = 3, 
                   position = "identity", alpha = 0.2, color = "black", fill = "green") +
    scale_x_continuous(limits = c(-90, -50))+
    scale_y_continuous(limits = c(0, 0.55))+
    xlab("Mean Sv") + 
    ylab("Proportion")+ 
    ggtitle(paste0("Cruise", " ", cruse, " ", "-", " ", seas, " ", yr))
  # print(g)
#   ggsave(png, g)
}

fig1 <- cruise_plot("1", "Central", "Winter", "2005")
fig2 <- cruise_plot("2", "Central","Winter", "2007")
fig3 <- cruise_plot("3", "Central","Summer", "2007")
fig4 <- cruise_plot("4", "Central","Winter", "2010")
fig6 <- cruise_plot("6", "Central","Winter", "2011")
fig7 <- cruise_plot("7", "Central","Summer", "2012")
fig8 <- cruise_plot("8", "Central","Summer", "2013")
fig9 <- cruise_plot("9", "Central","Winter", "2014")
fig10 <- cruise_plot("10", "Central","Summer", "2014")
fig11 <- cruise_plot("11", "Central","Summer", "2016")
fig12 <- cruise_plot("12", "Central","Summer", "2017")

multiplot(fig1, fig2, fig3, fig4, fig6, fig7, fig8, fig9, fig10, fig11, fig12, cols = 3)

```

##### ANOVA model subsetted by region:Central (Sv_mean ~ cruise)
```{r anova_central}
acousticdata_Central = subset(acousticdata, region == "Central")
acousticdata_Central$cruise = as.factor(acousticdata_Central$cruise)

aov.acoustics.sv2 <- aov(Sv_mean ~ cruise, data = acousticdata_Central)
summary(aov.acoustics.sv2)

TukeyHSD(aov.acoustics.sv2)
```

##### Mean Sv by region, by cruise : Northern

```{r by_region_northern, echo = FALSE, warning = FALSE, message=FALSE, fig.width=9, fig.height=9}
cruise_plot <- function(cruse, reg, seas, yr){ # cntry <- "Canada"
  
  #browser()
#   png <- paste0("cruise", cruse, ".png")
#   cat("cruise_plot(", cruse, ") -> ", png, "\n")
#   
  g <- acousticdata %>%
    filter(cruise == cruse) %>%
    filter(region == reg) %>% 
    ggplot(aes(x=Sv_mean, group = cruise)) +
    geom_histogram(aes(y = ..count../sum(..count..)), binwidth = 3, 
                   position = "identity", alpha = 0.2, color = "black", fill = "yellow") +
    scale_x_continuous(limits = c(-90, -50))+
    scale_y_continuous(limits = c(0, 0.55))+
    xlab("Mean Sv") + 
    ylab("Proportion")+ 
    ggtitle(paste0("Cruise", " ", cruse, " ", "-", " ", seas, " ", yr))
  # print(g)
#   ggsave(png, g)
}

fig1 <- cruise_plot("1", "Northern", "Winter", "2005")
fig2 <- cruise_plot("2", "Northern","Winter", "2007")
fig3 <- cruise_plot("3", "Northern","Summer", "2007")
fig4 <- cruise_plot("4", "Northern","Winter", "2010")
fig6 <- cruise_plot("6", "Northern","Winter", "2011")
fig7 <- cruise_plot("7", "Northern","Summer", "2012")
fig8 <- cruise_plot("8", "Northern","Summer", "2013")
fig9 <- cruise_plot("9", "Northern","Winter", "2014")
fig10 <- cruise_plot("10", "Northern","Summer", "2014")
fig11 <- cruise_plot("11", "Northern","Summer", "2016")
fig12 <- cruise_plot("12", "Northern","Summer", "2017")

multiplot(fig1, fig2, fig3, fig4, fig6, fig7, fig8, fig9, fig10, fig11, fig12, cols = 3)

```

##### ANOVA model subsetted by region:Northern (Sv_mean ~ cruise)
```{r anova_north}
acousticdata_Northern = subset(acousticdata, region == "Northern")
acousticdata_Northern$cruise = as.factor(acousticdata_Northern$cruise)

aov.acoustics.sv2 <- aov(Sv_mean ~ cruise, data = acousticdata_Northern)
summary(aov.acoustics.sv2)

TukeyHSD(aov.acoustics.sv2)
```


#### To examine changes in vertical distribution of signal, data were re-extracted in 4 vertical bins (10-50m, 50-100m, 100-150m, 150-200m) for every km of cruise track.

##### of the 21827 km of cruisetack sampled, 18070 had data from all 4 vertical layers and are included below.

```{r get_50m_data , include = FALSE}
## read data
acousticdata50 = read.csv("~/Documents/R/Dosidicus/acoustics/portner_capegolcas_upper200m_by50m.csv")

### remove intervals which do not have all four layers ###
test_200m = aggregate(Layer~Interval*cruise, acousticdata50, sum)
colnames(test_200m) = c("Interval", "cruise", "Layersum")
test_200m_10 = subset(test_200m, Layersum==10)
test_merge_200m = merge(test_200m_10, acousticdata50,  by = c("Interval", "cruise"))

acousticdata50 <- test_merge_200m

test = aggregate(propNASC~cruise*region*Layer, acousticdata50, mean)
test$cpoly = paste(test$cruise, test$region, sep = "_")
test$Layer = as.factor(test$Layer)

```


```{r plot_propNASC_by_layer, echo = FALSE, fig.width=8}
cruisePoly <- ggplot(test, aes(cpoly, propNASC,col = Layer, pch = region)) + geom_point(size=3) + scale_color_brewer(palette = "RdYlBu")
cruisePoly = cruisePoly +scale_x_discrete(labels = cruises)+theme(axis.text.x=element_text(hjust=1))
cruisePoly = cruisePoly + labs(x="Cruise (Season.Year, where W = winter and S = summer)")+ggtitle("Proportion of NASC in each vertical 50m Layer (Layer 1 = 10-50m)")
cruisePoly

```

##### ANOVA model: (NASC ~ cruise*layer)
```{r anov, echo = FALSE}

acousticdata50$Layer = as.factor(acousticdata50$Layer)
acousticdata50$cruise = as.factor(acousticdata50$cruise)
acousticdata50$region = as.factor(acousticdata50$region)

aov.acoustics.nasc <- aov(NASC ~ cruise*Layer*region, data = acousticdata50)
summary(aov.acoustics.nasc)

```

##### It looks like there is a decrease in the propotion of signal in the upper 50 and an increase between 50 and 100m. To explore "trend" further, data were extrated from upper 100m in 10m bins (10-100m = 9 layers).

##### of the 21827 km of cruisetack sampled, 19727 had data from all 9 vertical layers in the upper 100m and are included below.

```{r get_10m_data , include = FALSE}
## read data
acousticdata10 = read.csv("~/Documents/R/Dosidicus/acoustics/portner_capegolcas_upper100m_by10m.csv") # "portner_acoustic_data_10-2017.csv"


depthdist = aggregate(NASC~Interval*cruise, acousticdata10, sum )
colnames(depthdist) = c("Interval", "cruise", "NASCsum")
acousticdata10 = merge(acousticdata10, depthdist, by = c("Interval", "cruise"))
acousticdata10$propNASC = acousticdata10$NASC/acousticdata10$NASCsum

acousticdata10$Layer = as.integer(acousticdata10$Layer)
### remove intervals which do not have all nine layers ###
test_100m = aggregate(Layer~Interval*cruise, acousticdata10, sum)
colnames(test_100m) = c("Interval", "cruise", "Layersum")
test_100m_10 = subset(test_100m, Layersum==45)
test_merge_100m = merge(test_100m_10, acousticdata10,  by = c("Interval", "cruise"))

# acousticdata10 = test_merge_100m

test = aggregate(propNASC~cruise*region*Layer, test_merge_100m, mean)
test$cpoly = paste(test$cruise, test$region, sep = "_")
test$Layer = as.factor(test$Layer)

```

```{r plot_propNASC_by_layer_10m, echo = FALSE, fig.width=8}
cruisePoly <- ggplot(test, aes(cpoly, propNASC,col = Layer, pch = region)) + geom_point(size=3) + scale_color_brewer(palette = "RdYlBu")
cruisePoly = cruisePoly +scale_x_discrete(labels = cruises)+theme(axis.text.x=element_text(hjust=1))
cruisePoly = cruisePoly + labs(x="Cruise (Season.Year, where W = winter and S = summer)")+ggtitle("Proportion of NASC in each vertical 10m Layer (Layer 1 = 10-20m)")
cruisePoly

```



```{r plot_depth_dist_by_region, echo = FALSE, fig.width=8, fig.height=21}
cruisePoly = cruisePoly+geom_line(aes(group=Layer))+facet_wrap(~region, ncol = 1)
cruisePoly
```


#### Baja 
```{r plot_depth_dist_by_region_boxplot_b, echo = FALSE, fig.width=20, fig.height=15}
acousticdata10 = subset(acousticdata10,Sv_mean > -900)

depth_plot <- function(lyr, rgn){ # cntry <- "Canada"
  
  #browser()
#   png <- paste0("cruise", cruse, ".png")
#   cat("cruise_plot(", cruse, ") -> ", png, "\n")
#   
  g <- acousticdata10 %>%
    filter(Layer == lyr) %>%
    filter(region == rgn) %>%
    ggplot(aes(cpoly, Sv_mean)) + 
    geom_boxplot() + scale_fill_brewer(palette = "RdYlBu")+
    scale_x_discrete(labels = cruises2)+
    labs(x="Cruise (Season.Year, where W = winter and S = summer)")+
    ggtitle(paste0("Boxplot of mean Sv in Layer"," ", lyr,  " ","for", " ", rgn))+ theme(legend.position="none")
 
  # print(g)
#   ggsave(png, g)
}

p1 <- depth_plot("1", "Baja")
p2 <- depth_plot("2", "Baja")
p3 <- depth_plot("3", "Baja")
p4 <- depth_plot("4", "Baja")
p5 <- depth_plot("5", "Baja")
p6 <- depth_plot("6", "Baja")
p7 <- depth_plot("7", "Baja")
p8 <- depth_plot("8", "Baja")
p9 <- depth_plot("9", "Baja")

multiplot(p1,p2,p3,p4,p5,p6,p7,p8,p9, cols = 3)

```


#### Sonora 
```{r plot_depth_dist_by_region_boxplot_s, echo = FALSE, fig.width=20, fig.height=15}
acousticdata10 = subset(acousticdata10,Sv_mean > -900)

depth_plot <- function(lyr, rgn){ # cntry <- "Canada"
  
  #browser()
#   png <- paste0("cruise", cruse, ".png")
#   cat("cruise_plot(", cruse, ") -> ", png, "\n")
#   
  g <- acousticdata10 %>%
    filter(Layer == lyr) %>%
    filter(region == rgn) %>%
    ggplot(aes(cpoly, Sv_mean)) + 
    geom_boxplot() + scale_fill_brewer(palette = "RdYlBu")+
    scale_x_discrete(labels = cruises2)+
    labs(x="Cruise (Season.Year, where W = winter and S = summer)")+
    ggtitle(paste0("Boxplot of mean Sv in Layer"," ", lyr, " ","for", " ", rgn))+ theme(legend.position="none")
 
  # print(g)
#   ggsave(png, g)
}

p1 <- depth_plot("1", "Sonora")
p2 <- depth_plot("2", "Sonora")
p3 <- depth_plot("3", "Sonora")
p4 <- depth_plot("4", "Sonora")
p5 <- depth_plot("5", "Sonora")
p6 <- depth_plot("6", "Sonora")
p7 <- depth_plot("7", "Sonora")
p8 <- depth_plot("8", "Sonora")
p9 <- depth_plot("9", "Sonora")

multiplot(p1,p2,p3,p4,p5,p6,p7,p8,p9, cols = 3)

```

#### Central 
```{r plot_depth_dist_by_region_boxplot_c, echo = FALSE, fig.width=20, fig.height=15}
acousticdata10 = subset(acousticdata10,Sv_mean > -900)

depth_plot <- function(lyr, rgn){ # cntry <- "Canada"
  
  #browser()
#   png <- paste0("cruise", cruse, ".png")
#   cat("cruise_plot(", cruse, ") -> ", png, "\n")
#   
  g <- acousticdata10 %>%
    filter(Layer == lyr) %>%
    filter(region == rgn) %>%
    ggplot(aes(cpoly, Sv_mean)) + 
    geom_boxplot() + scale_fill_brewer(palette = "RdYlBu")+
    scale_x_discrete(labels = cruises2)+
    labs(x="Cruise (Season.Year, where W = winter and S = summer)")+
    ggtitle(paste0("Boxplot of mean Sv in Layer"," ", lyr, " ","for", " ", rgn))+ theme(legend.position="none")
 
  # print(g)
#   ggsave(png, g)
}

p1 <- depth_plot("1", "Central")
p2 <- depth_plot("2", "Central")
p3 <- depth_plot("3", "Central")
p4 <- depth_plot("4", "Central")
p5 <- depth_plot("5", "Central")
p6 <- depth_plot("6", "Central")
p7 <- depth_plot("7", "Central")
p8 <- depth_plot("8", "Central")
p9 <- depth_plot("9", "Central")

multiplot(p1,p2,p3,p4,p5,p6,p7,p8,p9, cols = 3)

```

#### Northern 
```{r plot_depth_dist_by_region_boxplot_n, echo = FALSE, fig.width=20, fig.height=15}
acousticdata10 = subset(acousticdata10,Sv_mean > -900)

depth_plot <- function(lyr, rgn){ # cntry <- "Canada"
  
  #browser()
#   png <- paste0("cruise", cruse, ".png")
#   cat("cruise_plot(", cruse, ") -> ", png, "\n")
#   
  g <- acousticdata10 %>%
    filter(Layer == lyr) %>%
    filter(region == rgn) %>%
    ggplot(aes(cpoly, Sv_mean)) + 
    geom_boxplot() + scale_fill_brewer(palette = "RdYlBu")+
    scale_x_discrete(labels = cruises2)+
    labs(x="Cruise (Season.Year, where W = winter and S = summer)")+
    ggtitle(paste0("Boxplot of mean Sv in Layer"," ", lyr, " ", "for", " ", rgn))+ theme(legend.position="none")
 
  # print(g)
#   ggsave(png, g)
}

# the 
p1 <- depth_plot("1", "Northern")
p2 <- depth_plot("2", "Northern")
p3 <- depth_plot("3", "Northern")
p4 <- depth_plot("4", "Northern")
p5 <- depth_plot("5", "Northern")
p6 <- depth_plot("6", "Northern")
p7 <- depth_plot("7", "Northern")
p8 <- depth_plot("8", "Northern")
p9 <- depth_plot("9", "Northern")

multiplot(p1,p2,p3,p4,p5,p6,p7,p8,p9, cols = 3)

```

```{r anova_model_10m_mods, echo = FALSE}
acousticdata10$season = as.factor(acousticdata10$season)
acousticdata10$region = as.factor(acousticdata10$region)
acousticdata10$year = as.factor(acousticdata10$year)
acousticdata10$cruise = as.factor(acousticdata10$cruise)
acousticdata10$Layer = as.factor(acousticdata10$Layer)
```
##### ANOVA model 10m: (NASC ~ cruise* Layer *region)

```{r anova_model_10m}
aov.acoustics.nasc <- aov(NASC ~ cruise*Layer*region, data = acousticdata10)
summary(aov.acoustics.nasc)

```


```{r plot_depth_dist_by_region_boxplot_nasc, echo = FALSE, fig.width=20, fig.height=15}
# acousticdata10 = subset(acousticdata10,log(NASC) < 12)
# 
# depth_plot_nasc <- function(lyr){ # cntry <- "Canada"
#   
#   #browser()
# #   png <- paste0("cruise", cruse, ".png")
# #   cat("cruise_plot(", cruse, ") -> ", png, "\n")
# #   
#   g <- acousticdata10 %>%
#     filter(Layer == lyr) %>%
#     ggplot(aes(cpoly, log(NASC), fill = region)) + 
#     geom_boxplot() + scale_fill_brewer(palette = "RdYlBu")+
#     scale_x_discrete(labels = cruises)+
#     theme(axis.text.x=element_text(hjust=1))+
#     labs(x="Cruise (Season.Year, where W = winter and S = summer)")+
#     ggtitle(paste0("Boxplot of log(NASC) in Layer"," ", lyr))+ theme(legend.position="none")
#  
#   # print(g)
# #   ggsave(png, g)
# }
# 
# p1 <- depth_plot_nasc("1")
# p2 <- depth_plot_nasc("2")
# p3 <- depth_plot_nasc("3")
# p4 <- depth_plot_nasc("4")
# p5 <- depth_plot_nasc("5")
# p6 <- depth_plot_nasc("6")
# p7 <- depth_plot_nasc("7")
# p8 <- depth_plot_nasc("8")
# p9 <- depth_plot_nasc("9")
# 
# multiplot(p1,p2,p3,p4,p5,p6,p7,p8,p9, cols = 3)

```